\documentclass[margin,line]{res}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[unicode=true,
            colorlinks=true,
            linkcolor=blue]{hyperref}
\hypersetup{urlcolor=BlueViolet} % Does not apply color to href's
\hypersetup{colorlinks,urlcolor=BlueViolet} % href's are correct, but navigation


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}
\newcommand{\link}[1]{\texttt{#1}}
\providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}


\name{Matthew Rocklin\vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
%=========INFO=========
\begin{tabular}{@{}p{2in}p{4in}}
{\it E-mail:}  mrocklin@gmail.com   & {\it webpage:} \href{https://matthewrocklin.com}{matthewrocklin.com} \\
\end{tabular}


%========= RESEARCH =========
\section{\sc Summary}

I build and maintain parallel computing infrastructure for Python.
I help maintain the open source ecosystem,
and lead Coiled, a tech startup in this space.
Most of my work is focused around Dask, a library for scalable computing in Python.

This is part of a broader effort to increase accessibility of numerical methods to science and policy practitioners.

%========= WORK EXPERIENCE ==========
\section{\sc Professional Experience}

%\vspace{-.3cm}
{\bf Coiled } \\
{\em Founder, CEO } \hfill {\bf 2020 - }\\
Build a company to provide data science and machine learning at scale.
Coiled provides both managed Python deployments based on Dask,
as well as partnerships to build out advanced machine learning platforms.

%\vspace{-.3cm}
{\bf NVIDIA} \\
{\em Systems Software Manager} \hfill {\bf 2018 - 2020}\\
Manage a team of engineers to build Dask+GPU accelerated data science stack.
Manage open source community relations.

%\vspace{-.3cm}
{\bf Anaconda Inc} \\
{\em Computational Scientist} \hfill {\bf 2014 - 2018}\\
Build software and communities to scale Python's data analytics ecosystem

%\vspace{-.3cm}
{\bf Sandia National Laboratory } - Livermore, CA\\
{\em Postdoctoral Researcher} \hfill {\bf 2013 - 2014}\\
Computation and analysis of large time evolving networks

%\vspace{-.3cm}
{\bf Berkeley Engineering and Research/4D Imaging} - Berkeley, CA\\
{\em Software Developer} \hfill {\bf 2003 - 2005}\\
Designed and constructed 3d-scanner based on structured light techniques.
Founding engineer of a startup engineering company.

%========= EDUCATION ==========
\section{\sc Education}
{\bf University of Chicago}, Chicago, IL\\
%{\em Department of Statistics}
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D, Computer Science \hfill {\bf 2013}
\item[] M.S. Computer Science \hfill {\bf 2011}
\end{list1}

{\bf University of California, Berkeley}, Berkeley, CA\\
%{\em Department of Mathematics and Statistics}
\vspace*{-.1in}
\begin{list1}
\item[] B.A., Physics, Mathematics, and Astronomy \hfill {\bf May 2007}
\end{list1}

%=========== Software ================
\section{\sc Software}

\input{software.tex}


%========= PUBLICATIONS ==========
\section{\sc Publications}

\input{publications.tex}


%=========== Footer ================
\end{resume}
\end{document}

